Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
fix grammar, add ack

In addition, those abstract abstract machines with unbounded stacks naturally correspond
to abstract definitional interpreters. We show that after refunctionalizing an AAM with an
unbounded stack (and utilizing the proper caching algorithm), the pushdown control-flow analysis
can be obtained.

@@

The function @analyze@ is also changed by calling a @reset@ operator around the function 
call of @aeval@ to set the delimiter. The afterwards updating on cache becomes sequential.

@@

%% TODO: Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  The authors are grateful to the anonymous reviewers for their 
  helpful comments, and they are further indebted to Olivier Danvy 
  for numerous invaluable comments on the draft.

>>>>

In addition, those abstract abstract machines with an unbounded stack naturally correspond
to abstract definitional interpreters. We show that after refunctionalizing an AAM with an
unbounded stack (and utilizing the proper caching algorithm), the pushdown control-flow analysis
can be obtained.

@@

The function @analyze@ is also changed by calling the @reset@ operator around the function 
call of @aeval@ to set the delimiter. The afterwards updating on cache becomes sequential.

@@

%% TODO: Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  The authors are grateful to the anonymous reviewers for their 
  helpful comments, and they are further indebted to Olivier Danvy 
  for numerous invaluable comments on the draft. We also thank
  Kimball Germane and David Sherratt for their feedback, and
  Thomas Gilray for the discussion on pushdown control-flow analysis.
